Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Minor edits

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
	ecosystem}. Images are opened from files as \texttt{NumPy}
	arrays. Functions of \texttt{scikit-image} transform image arrays
	into other arrays with the same dimensions, or into arrays of
	numbers corresponding to features of the image. The output of
	scikit-image functions can be passed to other Python modules
	relying on \texttt{NumPy} arrays, such as \texttt{SciPy} or
	\texttt{scikit-learn}. Image-shaped arrays are transformed into
	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
	(3D). A variety of environments is available for code development
	and execution, from classical IDEs to Jupyter notebooks.
    \label{fig:ecosystem}}
\end{figure*}

@@

A stack of 2-D images, such as tomography slices generated by a reconstruction algorithm, can be opened as an image collection or a 3-D array:
\lstinputlisting[language=Python]{io_coll.py}
Raw data formats can be opened using the \texttt{NumPy} functions
\texttt{fromfile} (to load the array into memory) or \texttt{memmap} (to
keep the array on disk). The following code creates an array from a
raw image file of unsigned 16-bit integers with a header of 1024 bytes 
\begin{lstlisting}
im = np.memmap('image.edf', shape=(2048, 2048), offset=1024, dtype=np.uint16)
\end{lstlisting}
For every raw data specification, it is thus very easy to write a reader
using \texttt{np.memmap} (see for example
\url{https://github.com/jni/python-redshirt}). 
\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
    \caption{\csentence{The Spyder IDE} integrates a text editor (with
	syntax highlighting), the IPython interpreter, as well as a panel
	for code introspection (online help, variable explorer, \dots).
 \label{fig:spyder}}
\end{figure*}

\begin{figure*}[ht!]
    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

\begin{figure}[ht]
    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
    \caption{Simple visualization realized with Mayavi.
 \label{fig:mayavi}}
\end{figure}

@@

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU. \texttt{scikit-image} is not
the best tool for ultrafast computations where the workflow is known
beforehand, simple and stable. However, it is an excellent tool for
exploring image data interactively and testing different algorithms -- an
important component of data processing in scientific work --, and its
speed of execution is good enough to process the Gb-sized tomographic
images in seconds to minutes.

>>>>

\begin{figure*}
    \centerline{\includegraphics[width=0.77\textwidth]{ecosystem_landscape}}
    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
	ecosystem}. Images are opened from files as \texttt{NumPy}
	arrays. Functions of \texttt{scikit-image} transform image arrays
	into other arrays with the same dimensions, or into arrays of
	numbers corresponding to features of the image. The output of
	scikit-image functions can be passed to other Python modules
	relying on \texttt{NumPy} arrays, such as \texttt{SciPy} or
	\texttt{scikit-learn}. Image-shaped arrays are transformed into
	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
	(3D). A variety of environments is available for code development
	and execution, from classical IDEs to Jupyter notebooks.
    \label{fig:ecosystem}}
\end{figure*}

@@

A stack of 2-D images, such as tomography slices generated by a reconstruction algorithm, can be opened as an image collection or a 3-D array:
\lstinputlisting[language=Python]{io_coll.py}
Raw data formats can be opened using the \texttt{NumPy} functions
\texttt{fromfile} (to load the array into memory) or \texttt{memmap} (to
keep the array on disk). The following code creates an array from a
raw image file of unsigned 16-bit integers with a header of 1024 bytes 
\begin{lstlisting}
im = np.memmap('image.edf', shape=(2048, 2048), offset=1024, dtype=np.uint16)
\end{lstlisting}
For every raw data specification, it is thus very easy to write a reader
using \texttt{np.memmap} (see for example
\url{https://github.com/jni/python-redshirt}). 
\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
%\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.

@@

\begin{figure*}[ht!]
    \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
    \caption{\csentence{The Spyder IDE} integrates a text editor (with
	syntax highlighting), the IPython interpreter, as well as a panel
	for code introspection (online help, variable explorer, \dots).
 \label{fig:spyder}}
\end{figure*}

\begin{figure*}[ht!]
    \centerline{\includegraphics[width=0.75\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}

@@

\begin{figure}[ht!]
    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
    \caption{Simple visualization realized with Mayavi.
 \label{fig:mayavi}}
\end{figure}

@@

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU. At the moment,
\texttt{scikit-image} is not the best tool for ultrafast computations
where the workflow is known beforehand, simple and stable. However, it is
an excellent tool for exploring image data interactively and testing
different algorithms -- an important component of data processing in
scientific work --, and its speed of execution is good enough to process
the gigabyte-sized tomographic images in seconds to minutes. Moreover,
multiprocessing capabilities of \texttt{scikit-image} should improve in
the future.
